\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2022-12-09 sections/chameleon.tex
Update bib

\section{Motivation}
The design requirements of \chameleon{} are motivated by limitations of traditional type errors, as documented in a number of studies (e.g.~\cite{yang_improved_2000}), but which we illustrate here with a few motivating examples. 
%These limitations are sourced from the authors' frustration in teaching and writing Haskell. This list of shortcomings of traditional type errors is also strengthened by multiple studies pursuing improvement\cite{yang_improved_2000}.

>>>>

\section{Motivation}
The design requirements of \chameleon{} are motivated by limitations of traditional type errors, as documented in a number of studies (e.g.~\cite{yang_improved_2000, hage_solved_2020}), but which we illustrate here with a few motivating examples. 
%These limitations are sourced from the authors' frustration in teaching and writing Haskell. This list of shortcomings of traditional type errors is also strengthened by multiple studies pursuing improvement\cite{yang_improved_2000}.
